Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2019-04-04 man/figures/nls_long_term_resilience.Rmd
add pvalue and rsquared

@@

@@

fe1 <- as.formula(rs ~ I(a*sev^b + c))
preview(fe1, data = d, start = list(a= 0.0015, b = 2, c=0.8))

e1 <- nls(fe1, data = d, start = list(a = 0.0015, b = 2, c=.8),
          trace = TRUE, control = list(maxiter = 100))
summary(e1)

>>>>

TE Quedaste por aquí. No acabaste de encontrar un NLS mejor que la LM

@@

d$ly <- log(d$rs)
d$lx <- log(d$sev)

summary(lm(ly~lx, data=d))

d$y <- log(d$rs-0.6)

@@

pF <- function(x,a,b,c) {
  I(a*x^b + c)
}

fe1 <- as.formula(rs ~ I(a*sev^b + c))
m1 <- nls(fe1, data = d, start = list(a=2.755, b=.00014, c=.85), 
          control = list(maxiter = 500), trace = TRUE)
summary(m1)
abline(lm(rs~sev, data=d), col="blue")

summary(lm(rs~sev, data=d))

grid.start <- expand.grid(list(
  a = seq(0.001, 0.03, by=0.001),
  b = seq(1.8, 2.2, by=0.01),
  c= c(0.8)))

m2 <- nls2(rs~pF(sev, a,b,c), data = d, 
          start = grid.start,
          algorithm = "brute-force")

preview(fe1, data = d, start = list(a= 0.5, b = 0.23, c=0.8))

e1 <- nls(fe1, data = d, start = list(a= 0.5, b = 0.18, c=0.8),
          trace = TRUE, control = list(maxiter = 100))
summary(e1)

### 2019-04-04 man/figures/resilience_long_term.Rmd
add pvalue and rsquared

  ggplot(df, aes_string(y=paste0(v, "_mean_mean"), x=x, label=label)) + 
    geom_smooth(method='lm', se=FALSE, colour="gray") +
    geom_errorbar(mapping = yerrbar) + 
    geom_point(size=1.5, pch = 21, colour="black", fill="white") + 
    theme_bw() + 
    geom_text_repel(nudge_x = 0.5, size = 3) + 
    annotate("text", x=coordX_eq, y = coordY_eq, 
             label=lm_eqn(lm(formulita, df)), parse=TRUE, 
             size = 4.5, fontface = "bold") +
    ggtitle(titulo) + 
    theme(plot.title = element_text(size = 11, face = "bold.italic"),
          panel.grid = element_blank(), 
          axis.text.y = element_text(size=9),
          axis.text.x = element_text(size=9),
          axis.title = element_text(size = 10))
  }

@@

```{r plot_rt}
sevRt <- plotrel(sdf, v = "rt", x = 'd_severity', label = 'disturb_year',
                 coordX_eq = 10, coordY_eq = 0.5, titulo = "Rt") +
  xlab('') + ylab('') +
  theme(plot.margin = margin(r=-0.7, l=0, t=0, b=0, "pt"))
```

```{r plot_rs}
sevRs <- plotrel(sdf, v = "rs", x = 'd_severity', label = 'disturb_year',
                 coordX_eq = 10, coordY_eq = 0.5, titulo = "Rs") + 
  xlab('') + ylab('') +
  theme(plot.margin = margin(r=0, l=-0.7, t=0, b=0, "pt"))
```

```{r plot_rc}
sevRc <- plotrel(sdf, v = "rc", x = 'd_severity', label = 'disturb_year',
                 coordX_eq = 10, coordY_eq = 0.5, titulo = "Rc") +
  xlab("Drought Severity") + ylab('') +
  theme(plot.margin = margin(r=-0.7, l=-0.7, t=0, b=0, "pt"))
```

@@

>>>>

  ggplot(df, aes_string(y=paste0(v, "_mean_mean"), x=x, label=label)) + 
    geom_smooth(method='lm', se=FALSE, colour="gray") +
    geom_errorbar(mapping = yerrbar) + 
    geom_point(size=1.5, pch = 21, colour="black", fill="white") + 
    theme_bw() + 
    geom_text_repel(nudge_x = 0.5, size = 3) + 
    annotate("text", x=coordX_eq, y = coordY_eq, 
             label=lm_eqn(lm(formulita, df)), parse=TRUE, 
             size = 4.5, fontface = "bold") +
    ggtitle(titulo) + 
    theme(plot.title = element_text(size = 11, face = "bold.italic"),
          panel.grid = element_blank(), 
          axis.text.y = element_text(size=9),
          axis.text.x = element_text(size=9),
          axis.title = element_text(size = 10))

  }

@@

```{r plot_rt}
sevRt <- plotrel(sdf, v = "rt", x = 'd_severity', label = 'disturb_year',
                 coordX_eq = 10, coordY_eq = 0.5, titulo = "Rt") +
  xlab('') + ylab('') +
  theme(plot.margin = margin(r=-0.7, l=0, t=0, b=0, "pt"))

summary(lm(rt_mean_mean~d_severity, data=sdf))
```

```{r plot_rs}
sevRs <- plotrel(sdf, v = "rs", x = 'd_severity', label = 'disturb_year',
                 coordX_eq = 10, coordY_eq = 0.5, titulo = "Rs") + 
  xlab('') + ylab('') +
  theme(plot.margin = margin(r=0, l=-0.7, t=0, b=0, "pt"))

summary(lm(rs_mean_mean~d_severity, data=sdf))
```

```{r plot_rc}
sevRc <- plotrel(sdf, v = "rc", x = 'd_severity', label = 'disturb_year',
                 coordX_eq = 10, coordY_eq = 0.5, titulo = "Rc") +
  xlab("Drought Severity") + ylab('') +
  theme(plot.margin = margin(r=-0.7, l=-0.7, t=0, b=0, "pt"))

glance(lm(rc_mean_mean~d_severity, data=sdf))
```

@@

```{r}
df <- sdf %>% 
  dplyr::select(d_severity, rt_mean_mean, rs_mean_mean, rc_mean_mean) %>% 
  gather(key = res_metric, value,c(rt_mean_mean,rs_mean_mean,rc_mean_mean))

nested_df <- group_by(df, res_metric) %>% nest()

fit_model <- function(df){
  lm(value ~ d_severity, data = df)
}

nested_df <- nested_df %>% 
  mutate(model = map(data, fit_model))

# Get R2 and p.value 
get_rsq <- function(mod) glance(mod)$r.squared
get_pvalue <- function(mod) glance(mod)$p.value

nested_df <- nested_df %>% 
  mutate(r.squared = map_dbl(model, get_rsq),
         pvalue = map_dbl(model, get_pvalue))
